\mytitle

### 2015-08-01 MSc_diss.tex
Changes in structure

\subsection{Alkyl nitrates}
\subsubsection{Alkyl nitrates chemistry}
(An example of such set of reactions is alkyl nitrate chemistry)

Alkyl nitrates ($RONO_2$) are organic tropospheric trace gases, which   due to one of their formation mechanisms are closely linked with the production of tropospheric ozone \citep{Reeves2007}.

@@

\subsubsection{Observational studies}

@@

\section{Literature review} \label{sec:data}
Alkyl nitrates ($RONO_2$) are organic tropospheric trace gases. They are produced photochemically through the oxidation of their parent hydrocarbons \citep{Roberts1990} or emitted directly from equatorial oceans \citep{Blake2003} and biomass burning \citep{Simpson2002}. Being involved in the ozone production chemistry, these species can act as reservoirs of nitrogen oxides which availability largely affects the production of ozone \citep{Reeves2007}. Since the alkyl nitrates have atmospheric lifetimes ranging from several days to about a month, they can redistribute nitrogen oxides presented over polluted continental regions to clean remote marine environments, and therefore are considered as one of the tracers for determining the anthropogenic influence \citep{Atherton1989, Reeves2007, Worton2005}.

@@

\subsection{Bertman}
Below is the simplified scheme of atmospheric hydrocarbon oxidation leading to the formation of alkyl nitrates (see also Fig. \ref{fig:scheme_bertman}). It begins from the process of $H$ abstraction by the $OH$ radical where the fraction of the primary or secondary radical is denoted by $\alpha_1$.
\begin{equation} \label{eq:alkane_oh}
RH + \bullet OH \xrightarrow{k_1, \alpha_1} R\bullet + H_2O
\end{equation}
The resulting radical rapidly reacts with $O_2$ and forms an alkyl peroxy radical ($R\bullet$):
\begin{equation} \label{eq:rad_o2}
R\bullet + O_2 \xrightarrow{k_2} ROO\bullet
\end{equation}
Then the alkyl peroxy radical reacts with $NO$, when it can either lose an oxygen atom to form alkoxy radical ($RO\bullet$) or bond with $NO$ to form an alkyl nitrate. The former reaction is a crucial in the net production of tropospheric ozone, since photolysis of $NO_2$ is the main photochemical source of $O_3$ in the troposphere.
\begin{subequations} \label{eq:peroxy_no0}
\begin{align}
ROO\bullet + NO &\xrightarrow{k_3, (1-\alpha_3)} RO\bullet + NO_2 \label{eq:peroxy_no1}\\
ROO\bullet + NO &\xrightarrow{k_3, \alpha_3} RONO_2 \label{eq:peroxy_no2}
\end{align}
\end{subequations}
In other words, a branching ratio $\alpha_3$ of the reactions between alkyl peroxy radicals and $NO$ leads to formation of nitrate products via rearrangement of a high-energy intermediate \citep{Bertman1995}. The branching ratio $\alpha_3$ is larger when the parent alkane is larger and is a function of temperature and pressure.

>>>>

\subsection{Alkyl nitrates}
Alkyl nitrates ($RONO_2$) are organic tropospheric trace gases, which   due to one of their formation mechanisms are closely linked with the production of tropospheric ozone \citep{Reeves2007}. This mechanism is present in the following section.

\subsubsection*{Alkyl nitrates chemistry}

@@

\subsubsection*{Bertman}
Below is the simplified scheme of atmospheric hydrocarbon oxidation leading to the formation of alkyl nitrates (see also Fig. \ref{fig:scheme_bertman}). It begins from the process of $H$ abstraction by the $OH$ radical where the fraction of the primary or secondary radical is denoted by $\alpha_1$.
\begin{equation} \label{eq:alkane_oh}
RH + \bullet OH \xrightarrow{k_1, \alpha_1} R\bullet + H_2O
\end{equation}
The resulting radical rapidly reacts with $O_2$ and forms an alkyl peroxy radical ($R\bullet$):
\begin{equation} \label{eq:rad_o2}
R\bullet + O_2 \xrightarrow{k_2} ROO\bullet
\end{equation}
Then the alkyl peroxy radical reacts with $NO$, when it can either lose an oxygen atom to form alkoxy radical ($RO\bullet$) or bond with $NO$ to form an alkyl nitrate. The former reaction is a crucial in the net production of tropospheric ozone, since photolysis of $NO_2$ is the main photochemical source of $O_3$ in the troposphere.
\begin{subequations} \label{eq:peroxy_no0}
\begin{align}
ROO\bullet + NO &\xrightarrow{k_3, (1-\alpha_3)} RO\bullet + NO_2 \label{eq:peroxy_no1}\\
ROO\bullet + NO &\xrightarrow{k_3, \alpha_3} RONO_2 \label{eq:peroxy_no2}
\end{align}
\end{subequations}
In other words, a branching ratio $\alpha_3$ of the reactions between alkyl peroxy radicals and $NO$ leads to formation of nitrate products via rearrangement of a high-energy intermediate \citep{Bertman1995}. The branching ratio $\alpha_3$ is larger when the parent alkane is larger and is a function of temperature and pressure.

\subsection{Ozone, alkyl nitrates and carbon bonds}

\section{Literature review} \label{sec:data}
\subsubsection{Observational studies}

@@

Alkyl nitrates ($RONO_2$) are organic tropospheric trace gases. They are produced photochemically through the oxidation of their parent hydrocarbons \citep{Roberts1990} or emitted directly from equatorial oceans \citep{Blake2003} and biomass burning \citep{Simpson2002}. Being involved in the ozone production chemistry, these species can act as reservoirs of nitrogen oxides which availability largely affects the production of ozone \citep{Reeves2007}. Since the alkyl nitrates have atmospheric lifetimes ranging from several days to about a month, they can redistribute nitrogen oxides presented over polluted continental regions to clean remote marine environments, and therefore are considered as one of the tracers for determining the anthropogenic influence \citep{Atherton1989, Reeves2007, Worton2005}.

@@
